---
title: Introduction
output: html_document
---

## Overview

*LACE* is an algorithmic framework that processes single-cell somatic mutation profiles from cancer samples collected at different 
time points and in distinct experimental settings, to produce longitudinal models of cancer evolution. The approach solves a Boolean Matrix 
Factorization problem with phylogenetic constraints, by maximizing a weighted likelihood function computed on multiple time points. 

```{r include=FALSE}
library(knitr)
opts_chunk$set(
concordance = TRUE,
background = "#f3f3ff"
)
```

## Installing LACE

The R version of *LACE* can be installed from Github. To do so, we need to install the R packages *LACE* depends on and the devtools package. 


```{r eval=FALSE}
# install LACE library
if (!require("devtools")) install.packages("devtools")
library("devtools")
install_github("BIMIB-DISCo/LACE", ref = "master")

# load LACE library
library("LACE")
```

## Debug

Please feel free to contact us if you have problems running our tool at daniele.ramazzotti1@gmail.com or d.maspero@campus.unimib.it. 
