---
title: "Introduction"
author: 
  - Daniele Ramazzotti
  - Fabrizio Angaroni
  - Davide Maspero
  - Alex Graudenxi
  - Luca De Sano
  - Gianluca Ascolani
date: "`r format(Sys.time(), '%B %d, %Y')`"
graphics: yes
package: LACE
output:
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{LACE,BiocStyle}
---

## Overview

*LACE* is an algorithmic framework that processes single-cell somatic mutation profiles from cancer samples collected at different 
time points and in distinct experimental settings, to produce longitudinal models of cancer evolution. The approach solves a Boolean Matrix 
Factorization problem with phylogenetic constraints, by maximizing a weighted likelihood function computed on multiple time points. 

```{r include=FALSE}
library(knitr)
opts_chunk$set(
concordance = TRUE,
background = "#f3f3ff"
)
```

## Installing LACE

The R version of *LACE* can be installed from BioConductor. To do so, we need to install the R packages *LACE* depends on and the devtools package. 


```{r eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("LACE")
```

## Debug

Please feel free to contact us if you have problems running our tool at daniele.ramazzotti1@gmail.com or d.maspero@campus.unimib.it. 
